A GPU Sonar Simulator for Automatic Target Recognition

### 2014-05-02 UAM2014/Article/article.tex
la2pdf commit - 2014:05:02	22:54:47	(Fri 2.May)

Automatic target recognition (ATR) is a fundamental component to optimize the use of autonomous underwater vehicles (AUVs), as it allows the vehicle to adapt its mission plan to e.g. revisit detected objects for closer examination. The ATR algorithms must, however, be sufficiently fast to process the sensor data onboard the AUV in delayed real-time.

Template matching is a common technique for classification of objects in synthetic aperture sonar (SAS) images. The principle is to isolate an image segment containing the object of interest, correlate it with a set of template images of the relevant object classes, and assign it to the class of the template yielding the highest correlation coefficient. The challenge is to come up with a representative set of template images covering the actual configurations of object and seabed. The use of a static, predetermined template library is often impractical and yield inaccurate results~\cite{Midelfart2010}.

@@

>>>>

Automatic target recognition (ATR) is an important component in autonomous underwater vehicles (AUVs), as it allows the vehicle to adapt its mission plan to e.g. revisit detected objects for closer examination. One way to classify these objects is by using template matching. The principle is to isolate an image segment containing the object of interest, correlate it with a set of template images of the relevant object classes, and assign it to the class of the template yielding the highest correlation coefficient. The challenge is to come up with a representative set of template images covering the actual configurations of object and seabed. The use of a static, predetermined template library is often impractical and yield inaccurate results~\cite{Midelfart2010}.

@@

% The ATR algorithms must, however, be sufficiently fast to process the sensor data onboard the AUV in delayed real-time.
